?????????????????

### 2022-11-09 article_1/article_1.tex
Add complex examples

\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination). This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem. In this way it is possible to estimate the direction of magnetization from multiple sources. The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}

@@

%%
\subsubsection{Direct Model}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{VECTORS.png}
\caption{Schematic representation of vector $h_j$ (\cref{eq:sphere8}) with elements $hx_j$, $hy_j$ and $hz_j$ in cartesian coordinates. This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ... L. Source: \cite{OliveiraJr.2015}.}
\label{fig:VECTORS}
\end{figure}

@@

\section{Conclusion}

>>>>

\noindent{The rapid inversion of the total field is a method developed by \cite{OliveiraJr.2015} being computationally efficient to invert the magnetic anomalies produced by multiple sources with approximately spherical shapes to estimate their magnetization directions (inclination and declination). This methodology requires the central position of the magnetic sources, which can be obtained with Euler Deconvolution, and the information on their geometry helps to reduce the non-exclusivity of the problem. In this way, it is possible to estimate the direction of magnetization from multiple sources. The method does not require that all sources have the same magnetization direction nor the use of regularly spaced data on a horizontal grid, and can still be implemented in linear and non-linear inversion problems.}

@@

%%
\subsubsection{Parametrization and Forward Model}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{VECTORS.pdf}
\caption{Schematic representation of vector $h_j$ (\cref{eq:sphere8}) with elements $hx_j$, $hy_j$ and $hz_j$ in cartesian coordinates. This vector has declination $D_j$ (positive clockwise) and slope $I_j$ (positive downwards), j = 1, 2, ... L. Source: \cite{OliveiraJr.2015}.}
\label{fig:VECTORS}
\end{figure}

@@

\section{Conclusion}
\noindent{We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the recovery of their magnetic moment. Being ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples. This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field. }

\noindent{We also present a new, faster and cleaner way to solve the Euler equation in determining the positioning of magnetic anomaly sources using a pre-selection of magnetic anomaly source windows based on the Laplacian of the Gaussian applied to total gradient anomaly maps. In this way, reducing the numerous solutions to just one data window per source. After estimating the structural index (N=3) by approximating the sources generating the magnetic anomaly to spheres/points, the Euler deconvolution is performed and the central position of each source is determined.}

\noindent{Since for the recovery of direction and magnetization we only need to assume that the sources have their central positions known (so we apply Euler deconvolution) and that their magnetizations are uniform. This last premise aligns with the theory of magnetically stable particles, which are the basis of classical paleomagnetism. Also, there is no need for any kind of prior knowledge other than the observed magnetic anomaly, and the structural index of the sources. Therefore, this method can be quickly replicated in a dataset of thin sections of rocks to obtain the distributions of magnetic directions of each source identified in the sample.}

\noindent{The test using a simply synthetic sample shows the great capability of the method by retrieving not only the precisely center positions }
